\documentclass[12pt]{article}
%Mathematical TeX packages from the AMS
\usepackage{amssymb,amsmath,amsthm} 
%geometry (sets margin) 
\usepackage[margin=1.25in]{geometry}
\usepackage{enumerate}
\usepackage{graphicx}
\def\ci{\perp\!\!\!\perp}
%=============================================================
%Redefining the 'section' environment as a 'problem' with dots at the end


\makeatletter
\newenvironment{problem}{\@startsection
       {section}
       {1}
       {-.2em}
       {-3.5ex plus -1ex minus -.2ex}
       {2.3ex plus .2ex}
       {\pagebreak[3] %basic widow-orphan matching
       \large\bf\noindent{Problem }
       }
       }
       {%\vspace{1ex}\begin{center} \rule{0.3\linewidth}{.3pt}\end{center}}
       \begin{center}\large\bf \ldots\ldots\ldots\end{center}}
\makeatother


%=============================================================
%Fancy-header package to modify header/page numbering 
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Brandon Sim}
\chead{} 
\rhead{\thepage} 
\lfoot{\small Computer Science 182} 
\cfoot{} 
\rfoot{\footnotesize Problem Set 3} 
\renewcommand{\headrulewidth}{.3pt} 
\renewcommand{\footrulewidth}{.3pt}
\setlength\voffset{-0.25in}
\setlength\textheight{648pt}
\setlength\parindent{0pt}
%=============================================================
%Contents of problem set

\begin{document}

\title{Computer Science 182: Problem Set 3, Written}
\author{Brandon Sim}

\maketitle

\textbf{Facts / Rules}
\begin{enumerate}
\item If someone is a man, he is mortal (All men are mortal).

$\forall x Man(x) \Rightarrow Mortal(x)$

\item Every man has exactly one (biological) mother. For every $x$, if $x$ is a man, then there exists a unique $y$, where $y$ is a woman and $y$ is the mother of $x$.

$\forall x Man(x) \Rightarrow \exists! y (Woman(y) \land MotherOf(y, x))$

\item If a woman is a mother of another person, then that other person has a mother.

$\forall x \exists y MotherOf(x, y) \Rightarrow HasMother(y)$

\item If someone is a mother, she is a woman (all mothers are women).

$\forall x Mother(x) \Rightarrow Woman(x)$

\item A maternal grandmother is the mother of a mother. For every $x$, if $x$ is a (maternal) grandmother, then there exists a $y$ who is a mother, where $x$ is the mother of $y$.

$\forall x MaternalGrandmother(x) \Rightarrow (\exists y MotherOf(x, y) \land Mother(y))$

\item A grandmother is the mother of a mother or a father. For every $x$, if $x$ is a grandmother (maternal or paternal), then there exists either a $y$ who is a mother, where $x$ is the mother of $y$, or there exists a $z$ who is a father, where $x$ is the mother of $z$.

$\forall x Grandmother(x) \Rightarrow (\exists y MotherOf(x,y) \land Mother(y)) \lor (\exists z MotherOf(x,z) \land Father(z))$

\item For all men with a mother, he has a (biological) father.

$\forall x (Man(x) \land HasMother(x)) \Rightarrow HasFather(x)$ 

\item If someone is a father, he is a man (all fathers are men).

$\forall x Father(x) \Rightarrow Man(x)$

\item If someone is a mother of someone else, they are related.

$\forall x \forall y MotherOf(x,y) \Rightarrow Related(x,y)$

\item If two people are married, they are not related.

$\forall x \forall y Married(x,y) \Rightarrow \lnot Related(x,y)$

\item If someone is a father of someone else, they are related.

$\forall x \forall y FatherOf(x,y) \Rightarrow Related(x,y)$

\item If a man has a father, the man is a son.

$\forall x HasFather(x) \Rightarrow IsSon(x)$

\end{enumerate}

\textbf{Another fact we can prove:}
If someone is a father, he is a son.

$\forall x Father(x) \Rightarrow IsSon(x)$

\textbf{Proof}: 

If someone is a father, he is a man (all fathers are men).

$\forall x Father(x) \Rightarrow Man(x)$

Every man has exactly one (biological) mother.

$\forall x Man(x) \Rightarrow \exists! y (Woman(y) \land MotherOf(y, x))$

If a woman is a mother of another person, then that other person has a mother.

$\forall x \exists y MotherOf(x, y) \Rightarrow HasMother(y)$

So, every man has a mother:

$\forall x Man(x) \Rightarrow HasMother(x)$

For all men with a mother, he has a (biological) father.

$\forall x (Man(x) \land HasMother(x)) \Rightarrow HasFather(x)$ 

Therefore, every man has a father:

$\forall x Man(x) \Rightarrow HasFather(x)$

If a man has a father, the man is a son.

$\forall x HasFather(x) \Rightarrow IsSon(x)$

\end{document}